### 2019-03-18 README.Rmd
Change README/vignette header levels, fix deploy
Deploy tweaks for images

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
cites_disconnect()
```

@@

### Citation

@@

### Contributing

@@

[![Created by EcoHealth Alliance](https://github.com/ecohealthalliance/citesdb/blob/master/inst/img/eha-footer.png)](https://www.ecohealthalliance.org/)

>>>>

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
cites_disconnect()
MonetDBLite::monetdblite_shutdown()
```

@@

## Citation

@@

## Contributing

@@

[![Created by EcoHealth Alliance](https://raw.githubusercontent.com/ecohealthalliance/citesdb/master/man/figures/eha-footer.png)](https://www.ecohealthalliance.org/)
